%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

\usepackage{xspace}

\newcommand{\db}{CrocodileDB\xspace}
\newcommand{\pg}{PostgreSQL\xspace}
\newcommand{\inqp}{InQP\xspace}
\newcommand{\iqp}{IQP\xspace}
\newcommand{\incability}{incrementability\xspace}
\newcommand{\Incability}{Incrementability\xspace}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Dixin Tang {\small (totemtang@berkeley.edu)}} % Print the main header

%------------------------------------------------
%
%\parbox{0.5\textwidth}{ % First block
%\begin{tabbing} % Enables tabbing
%\hspace{2.5cm} \= \hspace{4cm} \= \kill % Spacing within the block
%{\bf Email} \> totemtang@berkeley.edu \\ % Address line 1
%\end{tabbing}}
%\hfill % Horizontal space between the two blocks
%\parbox{0.5\textwidth}{ % Second block
%\begin{tabbing} % Enables tabbing
%\hspace{2.5cm} \= \hspace{4cm} \= \kill % Spacing within the block
%{\bf Address} \> Work from home 
%%{\bf Email} \> totemtang@berkeley.edu \\ % Email address 
%\end{tabbing}}
\vspace{-10mm}
%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Research Areas}

Interactive Data Analysis, Query Processing/Optimization, Cloud Database, Transaction Processing

\vspace{-5mm}

\section{Employment}

\tabbedblock{
    {2021-present} \> Postdoc Researcher - University of California, Berkeley \\[5pt]
    \> Advisor: Aditya G. Parameswaran
}

\vspace{-7mm}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
    {2015-2020} \> Ph.D. in Computer Science - University of Chicago \\[5pt]
    \> Advisor: Aaron J. Elmore \\[5pt]
    {2011-2014} \> M.S. in Computer Science - Institute of Computing Technology, Chinese Academy of Sciences \\[5pt]
    \> Advisor: Wei Li \\[5pt]
    {2007-2011} \> B.S. in Software Engineering - Huazhong University of Science \& Technology 
}

\vspace{-5mm}

%----------------------------------------------------------------------------------------
%	Publication SECTION
%----------------------------------------------------------------------------------------
\section{Recent Publications}
\pubgroup{
    \pub{Flexible Rule-Based Decomposition and Metadata Independence in Modin: A Parallel Dataframe System}
    	\> Devin Petersohn*, \textbf{Dixin Tang}*, Rehan Durrani, Areg Melik-Adamyan, Joseph E. Gonzalez, \\
    	\> Anthony D. Joseph, Aditya G. Parameswaran \\
    	\> \textbf{VLDB 2022} (*Equal contribution) \\[5mm]

    \pub{Lux: Always-on Visualization Recommendations for Exploratory Dataframe Workflows}
    	\> Doris Jung-Lin Lee, \textbf{Dixin Tang}, Kunal Agarwal, Thyne Boonmark, Caitlyn Chen, Jake Kang, \\
    	\> Ujjaini Mukhopadhyay, Jerry Song, Micah Yong, Marti A. Hearst, Aditya G. Parameswaran \\
    	\> \textbf{VLDB 2022} \\[5mm]

    \pub{Enhancing the Interactivity of Dataframe Queries by Leveraging Think Time}
    	\> Doris Xin, Devin Petersohn, \textbf{Dixin Tang}, Yifan Wu, Joseph E. Gonzalez, Joseph M. Hellerstein,  \\
    	\> Anthony D. Joseph, Aditya G. Parameswaran \\
    	\> \textbf{IEEE Data Eng. Bull. 2021} \\[5mm]

    \pub{Resource-efficient Shared Query Execution via Exploiting Time Slackness}
    	\> \textbf{Dixin Tang}, Zechao Shang, William Ma, Aaron J. Elmore, Sanjay Krishnan \\
    	\> \textbf{SIGMOD 2021} \\[5mm]

    \pub{CIAO: An Optimization Framework for Client-Assisted Data Loading}
    	\> Cong Ding, \textbf{Dixin Tang}, Xi Liang, Aaron J. Elmore, Sanjay Krishnan \\
    	\> \textbf{ICDE 2021, Short Paper} \\[5mm]
    	
    \pub{\db in Action: Resource-Efficient Query Execution by Exploiting Time Slackness}
       \> \textbf{Dixin Tang}, Zechao Shang, Aaron J. Elmore, Sanjay Krishnan, Michael J. Franklin \\
       \> \textbf{VLDB 2020, Demo} \\[5mm]

    \pub{Thrifty Query Execution via \Incability}
       \> \textbf{Dixin Tang}, Zechao Shang, Aaron J. Elmore, Sanjay Krishnan, Michael J. Franklin \\
       \> \textbf{SIGMOD 2020} \\[5mm]

    \pub{\db: Efficient Database Execution through Intelligent Deferment}
    \> Zechao Shang, Xi Liang, \textbf{Dixin Tang}, Cong Ding, Aaron J. Elmore, Sanjay Krishnan, Michael J. Franklin \\
    \> \textbf{CIDR 2020} \\[5mm]


    \pub{Intermittent Query Processing}
       \> \textbf{Dixin Tang}, Zechao Shang, Aaron J. Elmore, Sanjay Krishnan, Michael J. Franklin \\
       \> \textbf{VLDB 2019} \\[5mm]

    \pub{Socrates: The New SQL Server in the Cloud}
       \> Panagiotis Antonopoulos, Alex Budovski, Cristian Diaconu, Alejandro Hernandez Saenz, Jack Hu, \\ 
	   \> Hanuma Kodavalla, Donald Kossmann, Umar Farooq Minhas, Naveen Prakash, Hugh Qu,  \\ 
	   \> Chaitanya Sreenivas Ravella, Krystyna Reisteter, Sheetal Shroti, \textbf{Dixin Tang}, Vikram Wakade \\
       \> \textbf{SIGMOD 2019} \\[5mm]

    \pub{Toward Coordination-free and Reconfigurable Mixed Concurrency Control}
       \> \textbf{Dixin Tang}, Aaron J. Elmore \\
       \> \textbf{USENIX'ATC 2018} \\[5mm]

    \pub{Adaptive Concurrency Control: Despite the Looking Glass, One Concurrency Control Does Not Fit All}
       \> \textbf{Dixin Tang}, Hao Jiang, Aaron J. Elmore \\
       \> \textbf{CIDR 2017}
}

\vspace{-5mm}


\section{Earlier Publications}
\pubgroup{
    \pub{A Case Study of Optimizing Big Data Analytical Stacks Using Structured Data Shuffling}
       \> \textbf{Dixin Tang}, Taoying Liu, Rubao Lee, Hong Liu, Wei Li \\
       \> \textbf{BigData Congress 2016} \\[5mm]

    \pub{SparkArray: An Array-Based Scientific Data Management System Built on Apache Spark}
       \> Wenjuan Wang, Taoying Liu, \textbf{Dixin Tang}, Hong Liu, Wei Li, Rubao Lee \\
       \> \textbf{NAS 2016} \\[5mm]

    \pub{A Case Study of Optimizing Big Data Analytical Stacks Using Structured Data Shuffling}
       \> \textbf{Dixin Tang}, Taoying Liu, Rubao Lee, Hong Liu, Wei Li \\
       \> \textbf{CLUSTER 2015, Short Paper} \\[5mm]   

    \pub{RHJoin: A Fast and Space-efficient Join Method for Log Processing in MapReduce}
       \> \textbf{Dixin Tang}, Taoying Liu, Hong Liu, Wei Li \\
       \> \textbf{ICPADS 2014} \\[5mm]

    \pub{Optimizing the Join Operation on Hive to Accelerate Cross-Matching in Astronomy}
       \> Liang Li, \textbf{Dixin Tang}, Taoying Liu, Hong Liu, Wei Li, Chenzhou Cui  \\
       \> \textbf{IPDPS Workshops 2014}
}

\vspace{-5mm}

\section{Industrial Experience}
\intern{Internship at Microsoft Research}{June 2018-Sep. 2018}
{Benchmarking Socrates}{Umar Farooq Minhas}
{Socrates is a new cloud-native database that decouples computation from storage. 
My internship job is to test the new database architecture of Socrates 
in the industrial setting, understand its performance bottlenecks, 
and propose optimization opportunities.}

\vspace{-5mm}

%----------------------------------------------------------------------------------------
%	SYSTEM BUILDING EXPERIENCE
%----------------------------------------------------------------------------------------

%\section{System Building Experience}
%
%\system{Multi-Query Optimization in SparkSQL}
%{I extend SparkSQL to support multi-query optimization for the full TPC-H test suite. 
%The framework takes Dataframe queries as input and generates a query plan 
%that shares the execution of all submitted queries. 
%I enhance each intermediate tuple during query execution to 
%additionally include the query IDs that the tuple is valid to 
%and modify SparkSQL operators to leverage this information 
%to support shared query execution.}
%
%\system{Complex Materialized View Maintenance in SparkSQL}
%{I extend SparkSQL to support maintaining materialized views with deletes and updates.
%The system supports complex materialized views that are beyond select-project-join-aggregate queries. 
%Specifically, the supported operators include select, project, aggregate, sort, materialize, distinct, 
%and joins (inner, outer, and anti join), and there is no ordering limit about these operators.}
%
%\system{Intermediate State Management in \pg}
%{I extend \pg to support materialized view maintenance with intermediate state management. 
%The modified \pg can selectively discard some intermediate states to save memory resources. 
%When a discarded state is required to process new data, the system can rebuild this state from saved intermediate states 
%to quickly update the materialized view.
%}
%
%\system{Adaptive Concurrency Control in Main-Memory Database}
%{I develop a key-value main-memory database which hosts several concurrency control protocols 
%including partition-based concurrency control, two-phase locking, and optimistic concurrency control protocols. 
%The database uses a machine learning model to adaptively apply a protocol to a partition of the database 
%and reconfigures protocols in response to workload changes.}
%
%
%\vspace{-5mm}

%\section{Mentoring Experience}

%\mentor{Cong Ding, Undergraduate}{July 2019-Present}
%{I mentor Cong Ding on client-assisted data loading project, 
%which exploits partial data loading to make data quickly available, but not heavily sacrifice query performance. 
%The research paper is under preparation.}

%\vspace{-5mm}

%----------------------------------------------------------------------------------------
% Research Projects
%----------------------------------------------------------------------------------------
\section{Recent Research Projects}

\project{Dataspread: A Scalable Spreadsheet System}{Jan. 2021-Present}
{Spreadsheets have found ubiquitous use by scientists, business and financial analysts, 
researchers, and lay users. However, spreadsheets cannot express complex operations (e.g., joins), 
cannot handle large datasets, do not support collaboration, and foster errors, redundancy, and stale data. 
On the other hand, relational databases are well-known to be powerful and scalable, but are not flexible, intuitive, and interactive.
DataSpread addresses these limitations by holistically unifying spread-sheets with databases: 
preserving spreadsheets as the front-end, and databases as the back-end.}

\project{Modin: A Scalable Dataframe System}{Jan. 2021-Present}
{Dataframes have become universally popular as a means to flexibly represent data 
in various stages of structure, and manipulate it using a rich set of operators---thereby becoming an essential tool in the data scientists' toolbox. However, dataframe systems, such as pandas, scale poorly---and are non-interactive on moderate
to large datasets. We develop Modin to address this scalability problem and maintain the familiar pandas APIs for data scientists.}

\project{Lux: Always-on Visualization Recommendationsfor Exploratory Data Science}{Jan. 2021-Present}
{Exploratory data science largely happens in computational notebooks with dataframe API, such as pandas, 
that support flexible means to transform, clean, and analyze data.
Yet, visually exploring data in dataframes remains tedious, requiring substantial programming effort for visualization 
and mental effort to determine what analysis to perform next. 
We propose Lux, an \emph{always-on} framework for accelerating visual insight discovery in data science workflows. 
When users print a dataframe in their notebooks, 
Lux recommends visualizations to provide a quick overview of the patterns and trends and suggests promising analysis directions.}

\project{\db: Resource-efficient Database Execution}{July 2019-Mar. 2021}
{\db is a new database for processing dynamic datasets (e.g. streaming tuples). 
It exploits intelligent deferment to achieve low resource consumption 
and high query performance at the same time. 
In \db, users can trade-off between resource consumption and query performance 
by specifying a maximally allowed time slackness 
between the data is ready and the corresponding query result is available to users. 
Our system integrates the slackness constraints along with information 
about new data and query structures into the query optimizer 
to unlock new resource-efficient query execution plans.}

\project{\Incability-aware Shared Query Execution}{Mar. 2020-Mar. 2021}
{This project studies shared execution across standing queries that access the same data, 
but have different performance requirements. 
Shared execution eliminates redundant work across queries to reduce computing resources. 
However, the shared plan needs to meet the highest performance requirement (i.e. the lowest query latency), 
which forces some participating standing queries to run more eagerly. 
Eager incremental executions 
increase total work which may offset the benefits of shared execution. 
This project considers the two factors together 
and finds efficient query plans that 
reduce redundant work across concurrent queries and also avoid the cost of eager incremental executions. 
}

\project{Client-assisted Data Loading}{July 2019-Dec. 2020}
{Data loading is a time-consuming process. 
We study lazily loading data to make data available earlier, but not heavily sacrifice query performance. 
We redesign the data loading process by actively pushing predicates of prospective queries into 
the clients (e.g. edge devices) to generate bit-vectors that indicate whether a tuple is valid for a predicate. 
These bit vectors are used to partially load data that is most frequently accessed by prospective queries. 
When queries access unloaded data, the system uses the bit-vectors as an index to accelerate the query execution 
by skipping irrelevant tuples.}

\project{\Incability-aware Query Processing}{Mar. 2019-June 2020}
{This project studies how to efficiently maintain non-positive standing queries. 
While starting a query early and incrementally maintain the query result 
can reduce the query latency, it increases total query work (i.e. CPU cycles), 
especially when the database eagerly maintains non-positive queries, 
because output tuples in earlier executions may be removed by later executions. 
Observing that incremental executions for different parts of a query 
increase different amounts of total work for the same reduced latency, 
We define a metric, \textit{\incability} to quantify the cost-effectiveness of incremental executions. 
Our system leverages this metric to decide the execution frequencies of different parts of a query, 
which is optimized to reduce total query work and also achieve low query latency.}

\project{Intermittent Query Processing}{Dec. 2017-Sep. 2019}
{This project studies how to maintain a standing query 
over an incomplete data set with the remaining data
arriving in an intermittent, yet predictable way. 
To process this data arrival pattern, 
we propose \textit{Intermittent Query Processing}(\iqp) 
that does not keep the query active all the time but releases some memory resources when there is no data to process. 
When the query has no data to process, 
\iqp leverages the information about incoming data to 
selectively keeps a subset of intermediate states that are most useful 
for processing new data within a memory budget. 
Therefore, \iqp achieves low latency of updating query results with limited memory consumption.}

\project{Adaptive Concurrency Control for Main-memory Database}{Sep. 2015-Nov. 2017}
{We build a main-memory database that supports adaptively mixing multiple forms of concurrency control with minimal overhead. 
This system decomposes the workload into partitions and 
selects a concurrency control protocol for each partition of workload that the protocol is optimized for, 
and during workload changes adaptively reconfigures the protocols online. 
The experiments show that this approach has a higher throughput than the single best protocol under workload changes.}

\section{Earlier Projects}
\project{Structured Data Shuffling for Big Data Analytical Stacks}{Nov. 2013-Jan. 2015}
{We build a structured data shuffling procedure that can leverage the semantics of SQL queries to apply efficient compression algorithms 
and discard unnecessary data during data shuffling.}

\project{A Fast and Space-efficient Join Method for Log Processing in MapReduce}{Sep. 2012-Nov. 2013}
{We design a join method that achieves high query performance with a small extra storage cost for log processing. 
It shuffles the log table to avoid huge storage consumption and optimizes the shuffle procedure to achieve high query performance.}

\vspace{-5mm}

%----------------------------------------------------------------------------------------
%       SERVICE SECTION
%----------------------------------------------------------------------------------------
\section{Professional Services}
\tabbedblock{
    Program Committee: SIGMOD'22 \\[5pt]
    Reviewer: IEEE VIS'21 \\[5pt]
}
\vspace{-5mm}

%----------------------------------------------------------------------------------------
%	AWARD SECTION
%----------------------------------------------------------------------------------------

\section{Honors \& Awards}

\tabbedblock{
    {2018} \> USENIX ATC'18 Student Travel Grant \\[5pt]
    {2016} \> University Unrestricted (UU) Fellowship - The University of Chicago \\[5pt]
    {2016} \> CERES 1st year Graduate Research Award - The University of Chicago
}
\vspace{-5mm}

\section{Teaching Assistant}

\tabbedblock{
    {Fall 2015} \> MPCS 51040 - C programming  \\[5pt]
    {Spring 2016} \> MPCS 52040 - Distributed Systems  \\[5pt]
    {Winter 2017} \> CMSC 23500 - Introduction to Database \\[5pt]
    {Winter 2018} \> CMSC 23500 - Introduction to Database  \\[5pt]
    {Winter 2019} \> CMSC 23500 - Introduction to Database  \\[5pt]
    {Winter 2020} \> CMSC 23500 - Introduction to Database  
}
\vspace{-5mm}

%\job
%{Sep 2011 -}{Present}
%{Lehman Brothers, 1234 Mario Park, San Francisco, CA, United States}
%{http://www.lehmanbrothers.com}
%{Senior Developer / Technical Team Lead}
%{Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis elementum nec dolor sed sagittis. Cras justo lorem, volutpat mattis lacus vel, consequat aliquam quam. Interdum et malesuada fames ac ante ipsum primis in faucibus.\\
%\rule{0mm}{5mm}\textbf{Technologies:} Ruby on Rails 2.3, Amazon EC2, NoSQL data stores, memcached, collaborative matching, Facebook Graph API.}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

\section{Referees}

\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{1.5cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Aditya G. Parameswaran \\ % Referee name
{\bf Affiliate} \> University of California, Berkeley \\ % Referee company
{\bf Position} \> Assistant Professor \\ % Referee job title 
{\bf Contact} \> adityagp@eecs.berkeley.edu % Referee contact information
\end{tabbing}}
\\
\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{1.5cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Aaron J. Elmore \\ % Referee name
{\bf Affiliate} \> University of Chicago \\ % Referee company
{\bf Position} \> Assistant Professor \\ % Referee job title 
{\bf Contact} \> aelmore@cs.uchicago.edu % Referee contact information
\end{tabbing}}
\\
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing}
\hspace{1.5cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Michael J. Franklin \\ % Referee name
{\bf Affiliate} \> University of Chicago \\ % Referee company
{\bf Position} \> Liew Family Chairman of Computer Science \\ % Referee job title 
{\bf Contact} \> mjfranklin@uchicago.edu % Referee contact information
\end{tabbing}}
\\
\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{1.5cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Sanjay Krishnan \\ % Referee name
{\bf Affiliate} \> University of Chicago \\ % Referee company
{\bf Position} \> Assistant Professor \\ % Referee job title 
{\bf Contact} \> skr@cs.uchicago.edu % Referee contact information
\end{tabbing}}
\\
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing}
\hspace{1.5cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Umar Farooq Minhas \\ % Referee name
{\bf Affiliate} \> Microsoft Research \\ % Referee company
{\bf Position} \> Principle Researcher \\ % Referee job title 
{\bf Contact} \> ufminhas@microsoft.com % Referee contact information
\end{tabbing}}
\\
\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{1.5cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Wei Li\\ % Referee name
{\bf Affiliate} \> Institute of Computing Technology \\ % Referee company
{\bf Position} \> Associate Professor \\ % Referee job title 
{\bf Contact} \> liwei@ict.ac.cn % Referee contact information
\end{tabbing}}
\hfill


%----------------------------------------------------------------------------------------

\end{document}
